### 2017-03-01 IROS17/theory2robAlgs.tex
updated algorithm

\begin{algorithm}[htb]
\caption{2ParticlePathFinder($r_1,r_2,g_1,g_2,L$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 $OptimalPathList$ contains all the paths sorted by their path length plus an admissible heuristic. 
 \State $OptimalPathList \gets \{ h(\{\},r_1,r_2,g_1,g_2  ) ,\{\},r_1,r_2\}$ 
\While {We have not reached the goal in the first element}
\State Pop the first element in $OptimalPathList$
\State Call Alg. \ref{alg:Wallup} for all the four walls.
\State Add the results to $OptimalPathList$
\State Sort($OptimalPathList$)
\EndWhile
\State \Return $moves$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{WallFrictionMoveUp($r_1,r_2,g_1,g_2,L, moves$)}\label{alg:Wallup}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 The array \emph{moves} is the current sequence of moves up to the current position.
 Assume $r_1.x < r_2.x$ and $r_1.y \geq r_2.y$. If not, mirror the coordinate frame and swap the robots, then undo the mirroring before returning.
 $\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(g_1, g_2) , (r_1, r_2)$ all at least $\epsilon$ distance from walls the goals and starting points have at least $\epsilon$ distance from each other.  
$m_1$ is the first move toward the wall or goal.
 $m_2$ is the second move adjusting $\Delta e$.
\State $\Delta e \gets (g_2 - g_1)- (r_2- r_1)$
\If {$\Delta e = (0,0)$} \Comment{base case}
\State $m_1  \gets g_2 -  r_2$
\State $moves \gets \{ moves,   m_1 \}$
\State \Return $\{h(moves, r_1,r_2,g_1,g_2), moves\}$
\EndIf
\If {$r_2.x - r_1.x - 1 + 2 \epsilon \leq  \Delta g.x \leq  1 ~\textbf{and}~r_2.y - r_1.y \leq \Delta g.y \leq  0$} \Comment{$\Delta g \in $ reachable region}
\State $m_1 = \left(\frac{1-r_1.y}{2-g_1.y-r_1.y} (g_1.x -r_1.x), 1-r_1.y \right)$
\If {$r_2.x + m_1.x >L$}
\State $m_1.x = 1- r_2.x$
\EndIf
\If {$r_2.x + m_1.x <0$}
\State $m_1.x = -r_2.x$
\EndIf
\Else 
\State $m_1 = (0, 1-r_1.y)$
\State $\Delta g \gets $ closest reachable $(\Delta x,\Delta y)$.
%Adjust $\Delta g_x$ and $\Delta g_y$ %\Comment{To go to the nearest $\Delta g_x$ and $\Delta g_y$}
%\State $\Delta g_x = r_2.x - r_1.x - 1 + 2 \epsilon
\EndIf
\State $moves \gets \{ moves,   m_1\}$
\State $r_1 = r_1 + m_1$ \textbf{and} $r_2 = r_2 + m_1$
\State $m_2 = \Delta g -  (r_2- r_1)$
\If {robots on each other or on the wall}
\State Add $\pm \epsilon$ to $m_2.x$
\EndIf
\State $moves \gets \{ moves,   m_2\}$
\State \Return $\{h(moves, r_1,r_2,g_1,g_2), moves\}$
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}[htb]
\caption{ { \sc 2-ParticlePathFinder}($r_1,r_2,g_1,g_2,L$)}\label{alg:optimalAlg}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 $PathList$ contains all the paths sorted by their path length plus an admissible heuristic. 
 \State  $PathList \gets \{\}$
 \State $P \gets   \{ h(\{\},r_1,r_2,g_1,g_2  ) ,\{\},r_1,r_2\} $ \Comment $P$ contains the admissible heuristic, the move sequence, and the current robot positions
\While {$P.r_1 \ne g_1$ \textbf{and} $P.r_2 \ne g_2$}
\For{ $\theta \in \{0^\circ, 90^\circ, 180^\circ, 270^\circ \}$ }
\State $(r_1,r_2,g_1,g_2) \gets$ {\sc Rotate}($P.r_1,P.r_2,g_1,g_2,\theta$)
\State $\{d, $ \parbox[t]{.3\linewidth}{%
 $moves, r_1,r_2\} \gets$\\
 {\sc  PlanMoveUp}($r_1,r_2,g_1,g_2,L, P.moves$)}
\State $(moves, r_1,r_2) \gets$ {\sc Rotate}($moves, r_1,r_2,-\theta$)
\State   {\sc Push} $\{d, moves, r_1,r_2\} $ onto $PathList$
\EndFor
\State {\sc Sort}($PathList$) \Comment sort by admissible heuristic
\State $P \gets $ {\sc Pop} first element of $PathList$
\EndWhile
\State \Return $moves$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{{\sc PlanMoveUp}($r_1,r_2,g_1,g_2,L, moves$)}\label{alg:Wallup}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 The array \emph{moves} is the current sequence of moves up to the current position.
 Assume $r_1.x < r_2.x$ and $r_1.y \geq r_2.y$. If not, mirror the coordinate frame and swap the robots, then undo the mirroring before returning.
 $\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(g_1, g_2) , (r_1, r_2)$ all at least $\epsilon$ distance from walls the goals and starting points have at least $\epsilon$ distance from each other.  
$m_1$ is the first move toward the wall or goal.
 $m_2$ is the second move adjusting $\Delta e$.
\State $\Delta e \gets (g_2 - g_1)- (r_2- r_1)$
\If {$\Delta e = (0,0)$} \Comment{base case}
\State $m_1  \gets g_2 -  r_2$
\State $moves \gets \{ moves,   m_1 \}$
\State $(r_1,r_2) \gets ${\sc ApplyMove}$(m_1,r_1,r_2)$
\State \Return $\{h(moves, r_1,r_2,g_1,g_2), moves,r_1,r_2\}$
\EndIf
\If {$r_2.x - r_1.x - 1 + 2 \epsilon \leq  \Delta g.x \leq  1 ~\textbf{and}~r_2.y - r_1.y \leq \Delta g.y \leq  0$} \Comment{$\Delta g \in $ reachable region}
\State $m_1 \gets \left(\frac{1-r_1.y}{2-g_1.y-r_1.y} (g_1.x -r_1.x), 1-r_1.y \right)$
\If {$r_2.x + m_1.x >L$}
\State $m_1.x \gets 1- r_2.x$
%\EndIf
\Else \textbf{ if} {$r_2.x + m_1.x < 0$}  \textbf{then}
\State $m_1.x \gets -r_2.x$
\EndIf
\Else 
\State $m_1 = (0, 1-r_1.y)$
\State $\Delta g \gets $ closest reachable $(\Delta x,\Delta y)$.
%Adjust $\Delta g_x$ and $\Delta g_y$ %\Comment{To go to the nearest $\Delta g_x$ and $\Delta g_y$}
%\State $\Delta g_x = r_2.x - r_1.x - 1 + 2 \epsilon
\EndIf
\State $moves \gets \{ moves,   m_1\}$
\State $(r_1,r_2) \gets ${\sc ApplyMove}$(m_1,r_1,r_2)$
\State $m_2 \gets \Delta g -  (r_2- r_1)$
\If {robots on each other \textbf{or} on the wall}
\State Add $\pm \epsilon$ to $m_2.x$ to avoid collision
\EndIf
\State $moves \gets \{ moves,   m_2\}$
\State $(r_1,r_2) \gets ${\sc ApplyMove}$(m_2,r_1,r_2)$
\State \Return $\{h(moves, r_1,r_2,g_1,g_2), moves,r_1,r_2\}$
\end{algorithmic}
\end{algorithm}
